Avoiding the Global Sort: \break A Faster Contour Tree Algorithm

### 2017-01-05 paint-contour-tree.tex
typo corrected

\begin{definition} \label{def:ripe} A vertex $v$ is \emph{ripe} if: for all $c \in \col(v)$, 
%$v$ is present in $T(\rep(c))$ and is also the highest vertex in this heap. 
if $v$ is in heap of $c$ then it is the highest vertex in that heap (using notation from \Sec{struct}, if $v\in T(\rep(c))$, then it is the highest in $T(\rep(c))$).
%%Also, for all $c \in \col(v) \setminus \fcol(v)$, $T(\rep(c))$ is empty.
\end{definition}

>>>>

\begin{definition} \label{def:ripe} A vertex $v$ is \emph{ripe} if: for all $c \in \col(v)$, 
%$v$ is present in $T(\rep(c))$ and is also the highest vertex in this heap. 
if $v$ is in the heap of $c$ then it is the highest vertex in that heap (using notation from \Sec{struct}, if $v\in T(\rep(c))$, then it is highest in $T(\rep(c))$).
%%Also, for all $c \in \col(v) \setminus \fcol(v)$, $T(\rep(c))$ is empty.
\end{definition}
